Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2020-12-20 manuscript/draft_rsfmri.Rmd
prepare extractions of anatomical regions, create tables

<!-- INFERENCE --> To ensure robustness of our results, we computed estimates with non-parametric test using Wild bootstrap with an unrestricted SwE on all contrasts of interest for clusterwise inference. 
Type C2 for small sample bias adjustment is applied before the bootstrap resampling as recommended in the SwE manual. 
In contrast to the parametric estimation, Wild Bootstrap avoids any parametric distributional assumptions (e.g. random field theory), and is unlike permutation based framework appropriate<!-- permutations don't work with multilevel data (dependencies)--> for longitudinal data.
Unlike the description in the preregistration, we used a cluster forming threshold of $p < 0.001$ for a more multiple comparison adjustment (instead of $p < 0.01)$, and $1000$ bootstraps due to required computation time (instead of 5000). Significant clusters are defined as family-wise error (FWE) corrected $p < 0.05$. <!-- Prereg: We will use Type 3 small samples bias adjustment and “Approx” option for estimating the degrees of freedom. We will use the Non-Parametric Wild Bootstrap approach with default parameters, 5000 bootstraps and clusterwise inference (cluster forming threshold of p<0.01). Significant clusters are defined as family-wise error - corrected p<0.05. -->

@@

tab_qc_fc <-
  knitr::kable(
    round(res,3),
    col.names = colnames(res),
    row.names = TRUE,
    format = "latex",
    booktabs = T,
    caption = "Summary of quality metrics for different denoising pipelines across conditions and time points")

@@

>>>>

<!-- INFERENCE --> To ensure robustness of our results, we computed estimates with non-parametric test using Wild bootstrap with an unrestricted SwE on all contrasts of interest for clusterwise inference. 
Type C2 for small sample bias adjustment is applied before the bootstrap resampling as recommended in the SwE manual. 
In contrast to the parametric estimation, Wild Bootstrap avoids any parametric distributional assumptions (e.g. random field theory), and is unlike permutation based framework appropriate<!-- permutations don't work with multilevel data (dependencies)--> for longitudinal data.
Unlike the description in the preregistration, we used a cluster forming threshold of $p < 0.001$ for a more multiple comparison adjustment (instead of $p < 0.01)$, and $1000$ bootstraps due to required computation time (instead of 5000). Significant clusters are defined as family-wise error (FWE) corrected $p < 0.05$. The anatomical localization of significant clusters was investigated with the SPM Anatomy toolbox, version 3 [@Eickhoff_2005].<!-- Prereg: We will use Type 3 small samples bias adjustment and “Approx” option for estimating the degrees of freedom. We will use the Non-Parametric Wild Bootstrap approach with default parameters, 5000 bootstraps and clusterwise inference (cluster forming threshold of p<0.01). Significant clusters are defined as family-wise error - corrected p<0.05. -->

@@

tab_qc_fc <-
  knitr::kable(
    round(res,3),
    col.names = colnames(res),
    row.names = TRUE,
    format = "latex",
    booktabs = T,
    linesep = "",
    caption = "Summary of quality metrics for different denoising pipelines across conditions and time points") %>%
    column_spec(c(2:6), width = "1.8cm")

@@

```{r tableBMImodel}
source("code/construct_FCtables.R")
TableList <- construct_FCtables()
tableBMImodel <- TableList[[1]]
tableBMImodel
```

```{r tableFDmodel, echo=FALSE}
tableFDmodel <- TableList[[2]]
tableFDmodel
```

```{r tableBMIFDmodel, echo=FALSE}
tableBMIFDmodel <- TableList[[3]]
tableBMIFDmodel
```
